---
title: "Tidy Tuesday 2020 Week 41"
subtitle: "NCAA Women's Basketball Tournament" 
author: "Emilie Campos"
date: "Last updated: `r Sys.Date()`"
output: 
   html_document:
     toc: true
     toc_float:
        collapsed: true
        smooth_scroll: true
     toc_depth: 3
     theme: "yeti"
     highlight: tango
     df_print: paged
     code_folding: hide
editor_options: 
  chunk_output_type: inline
---

```{r Setup, include = FALSE}
# install and load required packages
if (!require("pacman")) 
  install.packages("pacman", repos = 'http://cran.us.r-project.org')
p_load(
  "tidyverse", # many useful packages :) 
  "here",      # file management 
  "tidytuesdayR", 
  "harrypotter"
)
p_load_gh("emjcampos/efuncs")

# set options for the whole document 
knitr::opts_chunk$set(
  fig.align = "center", 
  message = FALSE, 
  warning = FALSE, 
  echo = TRUE,
  out.width = "60%", 
  fig.show = "hold"
)

# source R scripts


# load Tidy Tuesday data 
# tt_data <- tt_load(2020, 41)
# write_rds(tt_data, here("2020", "week-40", "tt_data.rds"))
tt_data <- readRDS(here("2020", "week-40", "tt_data.rds"))
tournament <- tt_data$tournament
```

# The Data 

*Briefly describe the dataset here. What information does it contain? How many observations are there, and how many variables?* 

There are 2092 observations of 19 variables containing information about the NCAA Women's Basketball Tournaments from `r min(tournament$year)` to `r max(tournament$year)`.

```{r, echo = FALSE}
tournament
```


## Data Dictionary

### `tournament.csv`
|variable |class |description |
|:--------|:-----|:----------------------------|
|year              |double    | Tournament year |
|school            |character | School name |
|seed              |double    | Seed rank |
|conference        |character | Conference name |
|conf_w            |double    | Conference wins |
|conf_l            |double    | Conference losses |
|conf_percent      |double    | Conference win/loss percent |
|conf_place        |character | Conference placement (ie, 1st, 2nd, etc) |
|reg_w             |double    | Regular season wins |
|reg_l             |double    | Regular season losses |
|reg_percent       |double    | Regular season win/loss percent|
|how_qual          |character | How qualified - Whether the school qualified with an automatic bid (by winning its conference or conference tournament) or an at-large bid |
|x1st_game_at_home |character | Whether the school played its first-round tournament games on its home court. |
|tourney_w         |double    | Tournament wins |
|tourney_l         |double    | Tournament games losses |
|tourney_finish    |character | Tournament finish - The round of the final game for each team. OR=opening-round loss (1983 only); 1st=first-round loss; 2nd=second-round loss; RSF=loss in the Sweet 16; RF=loss in the Elite Eight; NSF=loss in the national semifinals; N2nd=national runner-up; Champ=national champions |
|full_w            |double    | Total sum of wins |
|full_l            |double    | Total sum of losses |
|full_percent      |double    | Total sum win/loss percent |


# Barplots 

*Make a barplot using using one or more categorical variables.*

```{r, out.width = "49%", fig.show = "hold", fig.align = "default"}
ggplot(tournament) + 
  geom_bar(aes(conf_w, fill = how_qual)) + 
  scale_fill_sherbert() + 
  labs(
    x = "Conference Wins", 
    y = "Count", 
    title = "Base theme", 
    fill = "How Qualified"
  )

ggplot(tournament) + 
  geom_bar(aes(conf_w, fill = how_qual)) + 
  theme_bw() + 
  scale_fill_sherbert(reverse = TRUE) + 
  labs(
    x = "Conference Wins", 
    y = "Count", 
    title = "theme_bw()", 
    fill = "How Qualified"
  )

ggplot(tournament) + 
  geom_bar(aes(conf_w, fill = how_qual)) + 
  theme_classic() +
  scale_fill_sherbert() + 
  labs(
    x = "Conference Wins", 
    y = "Count", 
    title = "theme_classic()", 
    fill = "How Qualified"
  )

ggplot(tournament) + 
  geom_bar(aes(conf_w, fill = how_qual)) + 
  theme_dark() + 
  scale_fill_sherbert(reverse = TRUE) + 
  labs(
    x = "Conference Wins", 
    y = "Count", 
    title = "theme_dark()", 
    fill = "How Qualified"
  )

ggplot(tournament) + 
  geom_bar(aes(conf_w, fill = how_qual)) + 
  theme_gray() + 
  scale_fill_sherbert() + 
  labs(
    x = "Conference Wins", 
    y = "Count", 
    title = "theme_gray()", 
    fill = "How Qualified"
  )

ggplot(tournament) + 
  geom_bar(aes(conf_w, fill = how_qual)) + 
  theme_light() + 
  scale_fill_sherbert(reverse = TRUE) + 
  labs(
    x = "Conference Wins", 
    y = "Count", 
    title = "theme_light()", 
    fill = "How Qualified"
  )

ggplot(tournament) + 
  geom_bar(aes(conf_w, fill = how_qual)) + 
  theme_minimal() + 
  scale_fill_sherbert() + 
  labs(
    x = "Conference Wins", 
    y = "Count", 
    title = "theme_minimal()", 
    fill = "How Qualified"
  )

ggplot(tournament) + 
  geom_bar(aes(conf_w, fill = how_qual)) + 
  theme_void() + 
  scale_fill_sherbert(reverse = TRUE) + 
  labs(
    x = "Conference Wins", 
    y = "Count", 
    title = "theme_void()", 
    fill = "How Qualified"
  )
```

*Provide a one-sentence interpretation of the main takeaway from the plot.*

# Boxplots 

*Make a boxplot using using one quantitative variable and at least one categorical variable.*

```{r}
ggplot(tournament) + 
  geom_boxplot(aes(x = conf_w, how_qual, fill = how_qual)) + 
  scale_fill_sherbert() + 
  theme(legend.position = "none") + 
  labs(
    x = "Conference Wins", 
    y = "How Qualified"
  )
```

*Provide a one-sentence interpretation of the main takeaway from the plot.*

# Scatterplots 

*Make a scatterplot using using two quantitative variables.*

*Provide a one-sentence interpretation of the main takeaway from the plot.*

# Your choice 

*Make a plot of your choosing. Provide a few sentences explaining the plot and the main takeaway conclusions.*